\subsection{Chris Pham}
\subsubsection{Fall}
\begin{itemize}
\item Week 1
\begin{itemize}
\item Activities
\begin{itemize}
\item Talked to the client to see if I can get into the OSURC Project
\end{itemize}
\item Summary
\begin{itemize}
\item I went ahead and looked through projects and then found a project that I liked, and then I emailed the stakeholder, Nick McComb, into adding me into his project.
\end{itemize}
\end{itemize}
\item Week 2
\begin{itemize}
\item Activities
\begin{itemize}
\item Emailed client when deciding to meet
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Client happened to be in California
\end{itemize}
\item Summary
\begin{itemize}
\item After being given our projects, we emailed our client and talked to our client over Slack to decide when to do our meeting about the project. We decided on Sunday for meeting up, while we think about the time schedule for the next assignments.
\end{itemize}
\end{itemize}
\item Week 3
\begin{itemize}
\item Activities
\begin{itemize}
\item Finishing Problem Statement
\item Started on Python Mastery 1
\end{itemize}
\item Summary
\begin{itemize}
\item I started working on my personal Problem Statement and was told from our client that we should do the Python Masteries. The client wanted to use it to prove that someone has enough understanding of the subject.
\end{itemize}
\end{itemize}
\item Week 4
\begin{itemize}
\item Activities
\begin{itemize}
\item Finished Problem Statement
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Python Mastery 1 is taking forever
\item Looking into alternatives to Code Academy.
\end{itemize}
\item Summary
\begin{itemize}
\item We worked on our collaborated Problem Statement and I started work on the Python 1 Mastery as suggested, but the actual website is expecting us to be completely new to coding. So in the end, I stopped because I was suffering while doing it. 
\end{itemize}
\end{itemize}
\item Week 5
\begin{itemize}
\item Activities
\begin{itemize}
\item Start on rough draft of the Requirements Document
\item Finished the draft, and it is uploaded to GitHub
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Ended up being sick
\item Could not finish the mastery program yet
\end{itemize}
\item Summary
\begin{itemize}
\item We worked on our rough draft of the Requirements Document and that is now submitted to GitHub. Client was wanting some changes on the Problem Statement, but we changed the document to reflect those changes.
\end{itemize}
\end{itemize}
\item Week 6
\begin{itemize}
\item Activities
\begin{itemize}
\item Finish the final draft of the Requirements Document
\item Sent to client for approval
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Issues with making the Gantt chart
\item Might need to start coding soon because the Mechanical team needs code
\end{itemize}
\item Summary
\begin{itemize}
\item We finished the Requirement Document and now I am thinking we are going to start on the project soon because we need to build parts of it for the mechanical engineering capstone group. 
\end{itemize}
\end{itemize}
\item Week 7
\begin{itemize}
\item Activities
\begin{itemize}
\item Divide up the section of the Tech Review Document into coherent sections
\end{itemize}
\item Summary
\begin{itemize}
\item After submitting our assignment last week about the Requirements document, we went ahead after our meeting to build our skeleton for the tech review. After build that, I could not do anything else because was finishing other homework and plan on starting more of the assignment during the weekend.
\end{itemize}
\end{itemize}
\item Week 8
\begin{itemize}
\item Activities
\begin{itemize}
\item Finish up rough draft of Tech Review Document
\item Gave our document to other people to review
\end{itemize}
\item Summary
\begin{itemize}
\item On Monday, I went ahead a my rough draft for the personal tech review. Then on Tuesday, we went ahead and reviewed someone else's document and got ours back on Thursday. Will probably finish final draft on Sunday.
\end{itemize}
\end{itemize}
\item Week 9
\begin{itemize}
\item Activities
\begin{itemize}
\item Finished final draft of Tech Review Document
\item Design document going to be started soon after
\end{itemize}
\item Summary
\begin{itemize}
\item On Monday, went and finished most of my tech review substance wise. On Tuesday, went ahead and tried to make it more readable.
\end{itemize}
\end{itemize}
\item Week 10
\begin{itemize}
\item Activities
\begin{itemize}
\item Finish working on Design Document in parts
\item Finish working on recording
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Everything ended up being due on Friday
\item Had to save this for last
\end{itemize}
\item Summary
\begin{itemize}
\item We started working on our design document on Thursday and then completed most of it during Friday because of lack of time and things like that. The video was done around that time too, couldn't do it in my house early in the day because of noises.
\end{itemize}
\end{itemize}
\end{itemize}
\subsubsection{Winter}
\begin{itemize}
\item{Week 1}
\begin{itemize}
\item Activities
\begin{itemize}
\item Created a working schedule because we have to work on campus for direct access
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item When thinking about implementing my area, was thinking of live tiling, or pre-stitched image after.
\end{itemize}
\item Summary
\begin{itemize}
\item After everyone got back from break, after class on Tuesday, we make a work schedule for us to work on the Rover. I was assigned the Mapping functionality of the ground station and some of the design decisions are up to me to choose.
\end{itemize}
\end{itemize}
\item{Week 2}
\begin{itemize}
\item Activities
\begin{itemize}
\item Start on turning last year's code into Object-oriented instead of procedural for ROS 
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Issues with big functions and converting them into stateful functions
\item Issues with downloading and speed of combining images into a single image
\end{itemize}
\item Summary
\begin{itemize}
\item I started on working the mapping core but I need to make the UI element and then try to make some speed improvements against PIL
\end{itemize}
\end{itemize}
\item{Week 3}
\begin{itemize}
\item Activities
\begin{itemize}
\item Working on adjusting maps in ways (Zoom/Scaling, Movement) 
\item A smaller image can be cut out of the bigger image now
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item PIL zoom does not work like I expected, might have to use QT's zoom
\end{itemize}
\item Summary
\begin{itemize}
\item Mapping is working mostly now with now a moving bounding box that goes in the big image and cuts what is needed.
\end{itemize}
\end{itemize}
\item{Week 4}
\begin{itemize}
\item Activities
\begin{itemize}
\item Map stitching works up to 3 miles before skew happens
\item Got items to place correctly onto the map and display correctly
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Somehow got issues with converting latitude and longitude into x, y coordinates gave me extreme values but got solved by pasting it again with a different name...
\item I was not able to do much work during the week because of the issue above
\end{itemize}
\item Summary
\begin{itemize}
\item In the end, I got mapping to work correctly to around 3 miles before my projection becomes skewed enough to become really inaccurate. I also got a way to map waypoints to a system, however that is my next problem because I actually have no way of removing them from the map itself. I think I might make another image to lay on top of the map and then clear out the box by doing the same command but making it transparent instead of coloring it.
\end{itemize}
\end{itemize}
\item{Week 5}
\begin{itemize}
\item Activities
\begin{itemize}
\item Implemented my mapping to work with the Qt interface
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Had issues with signals and slots for my listener because it would stall out when trying to paste the image, had to create another thread to handle that.
\item Had slight issues with trying to merge my branch because the repository's folder structure had changed so much
\end{itemize}
\item Summary
\begin{itemize}
\item This week I was trying to setup my class to properly implement with my Qt Application. That was real questionable but I think I can fix it using some type of class constructor call in an Qobject instead of instantiating it from the map object itself. Another thing I did was integrated my fork/branch into the main branch and it looks way better now. Feels pretty good actually.
\end{itemize}
\end{itemize}
\item{Week 6}
\begin{itemize}
\item Activities
\begin{itemize}
\item Worked on displaying the map correctly without massive hangups
\item Worked on our capstone paper and video
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Issues with scheduling for working, but in the end we worked on our own mostly and then worked online when we needed to.
\end{itemize}
\item Summary
\begin{itemize}
\item Worked on the poster, video, and displaying images on the GUI. Productive I say.
\end{itemize}
\end{itemize}
\item{Week 7}
\begin{itemize}
\item Activities
\begin{itemize}
\item Nothing
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Was way too busy with midterms 
\end{itemize}
\item Summary
\begin{itemize}
\item I did nothing at all. Feels bad man.
\end{itemize}
\end{itemize}
\item{Week 8}
\begin{itemize}
\item Activities
\begin{itemize}
\item Worked on some GPS/Waypoint handling for the map
\item Helped with recording for the club
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Overlay not working correctly, need to fix paste functionality
\end{itemize}
\item Summary
\begin{itemize}
\item Worked on the GPS and waypoint system, and for the club itself, I helped with filming and recording for the system reviews report needed.
\end{itemize}
\end{itemize}
\item{Week 9}
\begin{itemize}
\item Activities
\begin{itemize}
\item Worked on an correctly producing my indicator
\item Fixed on pasting the overlay image
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Was busy during Monday-Wends with plumber issues needing me to be home
\end{itemize}
\item Summary
\begin{itemize}
\item Fixed up my mapping and started working on integrating a waypoint system
\end{itemize}
\end{itemize}
\item{Week 10}
\begin{itemize}
\item Activities
\begin{itemize}
\item Built a intermediate system to handle button presses for way-point lists.
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item QT is really finicky with some function names and changes from Qt4 to Qt5 made some things harder to find 
\end{itemize}
\item Summary
\begin{itemize}
\item During the start of the term, I personally did not work on much because of issues with registration 
However, we did work out when we are expecting to work and meet up this term, which would be on Thursdays around 10 o'clock in the morning.
\end{itemize}
\end{itemize}
\end{itemize}
\subsubsection{Spring}
\begin{itemize}
\item Week 1
\begin{itemize}
\item Activities
\begin{itemize}
\item Meet up with the group to plan meetup times
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Issues in trying to get into classes
\end{itemize}
\item Summary
\begin{itemize}
\item After meeting up and trying to find 
\end{itemize}
\end{itemize}
\item Week 2
\begin{itemize}
\item Activities
\begin{itemize}
\item Finish integrating the GUI elements like buttons
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Issues with DMS conversions
\end{itemize}
\item Summary
\begin{itemize}
\item This week, I worked on completing the integration of the GUI. It turned out last term, that the East/West portion of the DMS conversion was not being set correctly. I spent a bit of time trying to get the correct float value to go down but then my minutes was completely off to the calculated DMS of the GPS location. Turns out that the box that contained the DMS location, would be limited to 0, 90, which actually needs to be 180 because it needs to span a half circle. Once that value was changed, the values were being set correctly.
\end{itemize}
\end{itemize}
\item Week 3
\begin{itemize}
\item Activities
\begin{itemize}
\item Finish up linking up buttons and interactions in the GUI
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item More issues with trying to get into the negative values of the DMS portion
\end{itemize}
\item Summary
\begin{itemize}
\item Turns out that I forgot to set the sign of the longitude and latitude to their corresponding North/South and East/West values. That was easily done using with many possible implementations like equalities, sign function in python, and other things like that.
\end{itemize}
\end{itemize}
\item Week 4
\begin{itemize}
\item Activities
\begin{itemize}
\item Finish up and submitting the poster
\item Edit documents to fit new the new competition
\end{itemize}
\item Summary
\begin{itemize}
\item This week, I was too busy to actually do much, and instead we worked on updating our documents to the new competition that we're going to now. And when that was done, we all just signed it and gave it to our client to sign. Also finished poster and it was sent to student media services.
\end{itemize}
\end{itemize}
\item Week 5
\begin{itemize}
\item Activities
\begin{itemize}
\item Finish working on multithreading and inputs.
\item Work on Midterm Report
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Was getting rate limited, needed to use a semaphore to limit thread usage.
\end{itemize}
\item Summary
\begin{itemize}
\item During Week 5, I worked on two important things, multi-threading the downloading of the image files from Google and integration of inputs into my mapping system. I was hitting issues with trying to use a pool but could not do it, in the end I needed to use processes. This in the ended up needing to be limited with semaphores so downloads could be regulated.
\item I also have started on integrating the GPS data that we are getting and applying that onto the map system that I've created. One problem is I forget how the data is formatted in the system and I need direct access to view the data that is being sent by the rover to parse correctly.
\end{itemize}
\end{itemize}
\item Week 6
\begin{itemize}
\item Activities
\begin{itemize}
\item Did not plan to do anything for Capstone at all.
\end{itemize}
\item Summary
\begin{itemize}
\item Did not do anything pertaining to Capstone at all.
\end{itemize}
\end{itemize}
\item Week 7
\begin{itemize}
\item Activities
\begin{itemize}
\item Present at Expo
\item Hunt for items that we need for Expo
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item Someone actually destroyed some motor nodes, so only 4 or the 6 wheel positions only move.
\item Corwin in the end, converted the connectors to USB and then connected those via USB.
\end{itemize}
\item Summary
\begin{itemize}
\item We met up on Thursday to find out what we actually need for Expo and what will be provided for Expo or not. It turned out that a Electrical team member blew a series of driver nodes, and had to build something to replace it. One method was making an emulator, or just run a newer number of nodes if the complete system cannot boot. It only turned out the controller boards only got fried, and so it had to get rigged to run off of USB. The day of Expo, we went to our position, and realized that we only had one table shared with the other Mars Rover Team Capstone project, and had to find the coordinator to get us another table. That was resolved, and then we went ahead and got all the stuff from the club room, and brought it to our table and presented.
\end{itemize}
\end{itemize}
\item Week 8
\begin{itemize}
\item Activities
\begin{itemize}
\item Nothing at all
\end{itemize}
\item Problems / Solutions
\begin{itemize}
\item With nothing working correctly, because of the blown electronics, other interfaces could not be used like the GPS information.
\end{itemize}
\item Summary
\begin{itemize}
\item Nothing could be done, with the lack of integrating parts from the rest of the rover team.
\end{itemize}
\end{itemize}
\item Week 9
\begin{itemize}
\item Activities
\begin{itemize}
\item Nothing at all
\end{itemize}
\item Summary
\begin{itemize}
\item Did nothing, because of other homework assignments taking my time.
\end{itemize}
\end{itemize}
\item Week 10
\begin{itemize}
\item Activities
\begin{itemize}
\item Started and finished the final video report and started on the final paper.
\end{itemize}
\item Summary
\begin{itemize}
\item We started our video on Thursday and finished on Friday, and then started working on this paper over the weekend. We are expecting to finish this whole document around Tuesday afternoon.
\end{itemize}
\end{itemize}
\end{itemize}