\section{Introduction}
\subsection{Who Requested the Project?}
This project was requested by the Oregon State University Robotics Club's (OSURC) Mars Rover team.

\subsection{Why Was the Project Requested?}
This project was requested due to the Mars Rover team's need for a complete and functional ground station in a time frame that the existing software team may not have been able to accomplish. Additionally, new requirements for the ground station meant that the increased complexity was most likely going to require a more dedicated team to complete than the volunteers the club normally has working on the Mars Rover project.

\subsection{What is the Importance of the Project?}
This project solves some of the most common problems for the Mars Rover team in previous competition years. Historically, the team is allowed a 10-15 minute set up time during competition where the Rover must be turned on, ground station connected, and core systems tested before actually competing in a task. In previous years, the Rover's ground station has normally been a laptop with a handful of random pieces of hardware plugged into it over USB. Many times, this hardware has been damaged during transit and caused problems during the setup phase. Additionally, previous software has often been command line driven and extremely specialized meaning the software is difficult to use, difficult to teach, and has ended up getting re-written with each new Rover competition year.

\subsection{Our Client and Their Role}
Our client was Nick McComb, team lead and electrical lead of the Mars Rover team for the 2017-2018 competition year. His role was mainly supervisory, helping our group set up the initial requirements for the software, and occasionally making requests for additional features as the year progressed. 

\subsection{Our Team Members and Roles}
\begin{itemize}
\item Chris Pham
	\begin{itemize}
    \item Rover mapping systems
	\end{itemize}
\item Ken Steinfeldt
	\begin{itemize}
    \item Rover status systems
	\end{itemize}
\item Corwin Perren
	\begin{itemize}
	\item Team Manager
    \item Rover video systems
    \item Program structure / startup
	\end{itemize}
\end{itemize}
