\subsection{Corwin Perren}
\subsubsection{Week 1}
The first week I spent catching up with Chris and Ken after the break to see where we were at for the term. Part of this was talking about the Mars Rover team changing to the Canadian International Rover Challenge over URC. The requirements for the competitions are near identical, and in fact removed some requirements over what URC desires. We made plans to update the design requirements document and poster to reflect these changes.

\subsubsection{Week 2}
During work on Thursday, I got SpaceNav mouse integration working and ready for Chris to integrate with mapping. As the Rover's arm was not yet ready, integration for arm control was not yet possible. This week I also registered our team for EXPO and dealt with getting signed release forms from Chris and Ken to send in. Per the previous week revelation that the team would be changing competitions, we worked through the new requirements to find out which exact ones needed to be modified in our design requirements document and then made an up to date list of all remaining work to be done.

\subsubsection{Week 3}
Week three I went back to working on some code for the Rover itself as the core of the ground station was done minus features that had missing Rover components. I mainly worked on modifying the Rover node that interfaced with the Rover's IRIS controller to get feedback about the Rover's battery voltage. I then updated the system\_statuses node to send this information to the ground station. I also helped a Rover team member do the same for GPS statuses. At the end of this week, I also made a new ROS package called rover\_arm to begin interfacing with the IONI motor drivers that the arm uses for control. I got a simple package compiling with the Simplemotion library and ROS packages and got an arm motor moving using the node. 

\subsubsection{Week 4}
This week I mainly took care of class and administrative work. Our team worked to make changes to the poster to reflect the challenge change as well as some minor wording and alignment changes. Additionally, we made changes to the design requirements document, signed off on the changes ourselves, had the stakeholder sign it, and sent it to the TA, professors, and stakeholder.

\subsubsection{Week 5}
This was my busy midterms week, so no project work was done. I did work on this midterm progress report and presentation though.


