\subsection{Ken Steinfeldt}
\subsubsection{Week 1}
The first week of the term. 
This is the week after spring break so the team meets to go over the status of the project and any of the changes that occured during the last two weeks.
The rover team is no longer going to compete in the University Mars Rover Challenge, but instead will now compete in the Canadian International Rover Challenge. 
Because of the change in competition some minor changes in requirements are needed, and these are discussed.
The general status of the project is also discussed, as well as new meeting times for the coming term.
\subsubsection{Week 2}
In week 2 Corwin wrangles the group into dealing with the required EXPO bureaucracy.
This includes registering the group itself for expo and signing release forms.
We also discuss changes required by the change in competition. 
These changes, as well as some general design changes made by the rover team, require some slight changes to the status readout on the GUI.
Adding these statuses to the StatusCore module isn't too bad but the status signals are not yet all built on the Rover side.
\subsubsection{Week 3}
Though Rover does not yet broadcast all of the necessary status updates, I start preparing for them.
This includes deprecating some old statuses that will no longer be used (the bogies, for example) and stubbing out new subscribers, etc.
Later this week Rover team adds new statuses to the rover. 
These new statuses will allow me to wrap up StatusCore in the future.
\subsubsection{Week 4}
Week four I continue to build the foundation for the new statuses. 
This week our final poster is finalized and submitted after being approved.
At this point all except the software is ready for Expo. 
The group also discussed and finalized necessary changes to the project requirements and had them signed off on by every team member as well as our client.
\subsubsection{Week 5}
During week five I am absolutely swamped with midterm exams and projects so I am not able to get much done on the ground station. 
I do meet with the team on Thursday, but I am unable to accomplish much.
This week also required that we write this midterm report as well as record the midterm report presentation.









