\subsection{Chris Pham}
\subsubsection{Technical Knowledge Gained}
From this project, I learned quite a bit of technical knowledge doing this project over the year.
I learned how to use Qt and ROS enough to build a system using it, do not think I can do it well though.
After working with a large code base, I've learned to link projects in a tried grouped faction, close to the next object.
I think I know how to remove very stateful code, and breaking it into helper functions and the main class.
With the use of image manipulation, I feel that I know how to exactly how to use PIL, OpenCV, and other image software to stitch a bunch of files.
\subsubsection{Non-Technical Knowledge Gained}
For this project, I think I gained more of a time regulating skill, where I would have to say, I could not contribute to a project for a period of time, instead of doing half time on both projects or more.
Another point, is learning to ask for expectations and goals, and then slightly passing them because extra work would be unnoticed, and/or unused by the team, but too little would produce an incomplete product.
\subsubsection{Knowledge Gained of Project Work}
From this project, I learned that when you expect that something will take a period of time, expect truly to take double that.
Another take from this project is that, with some other projects that rely in other parts by other people, try to make something, and you could always try to fix it later.
Goals will always change, and be ready to change on a dime.
And in the end, without any type of leader or management, time will always be hard to come by, and everything will possibly be late.
\subsubsection{Knowledge Gained of Project Management}
For our group, there was not much of a need to police what someone did or did not do.
In the end, our biggest problem was the time commitments from having a group member in Hillsboro and only down Tuesday or Thursday which made some activities like weekend meetings near impossible.
\subsubsection{Knowledge Gained of Working in Teams}
For the group, we all had fun with each other and everyone else in the team and that made communications very easy to do.
Everyone was free form, and we did whatever we needed and the others would be accommodating in trying to fit that schedule.
When we could not meetup, we could at least use other means of communications like Slack to talk about expectations and code, which allowed for us do to whatever we need to do.
\subsubsection{Changes to Make if Starting Over}
If we were to start this over, I would like to some things to allow us to succeed further.
I think we would all make better plans at the start to allow for missteps of the team, and allow for easier prototyping.
That prototyping can allow for delays in the team, and then can be built with expected values instead of waiting for the system to be built.
Another thing would be getting testing data that we can use for integrated tests like GPS, Video, and Statuses, so we can just build a system using that data then it should be the same on the complete system.
I think for my section, I would actually use OpenGL instead of the PIL mapping system, because translating numbers randomly feels very weird, compared to my graphics history.