\subsection{Deliverables}
\subsubsection{Github Repository}
Our group gained access to and set up directories in the Github repository for storing the group's ground station code and documentation.
All documentation was put into this repository as it was started and/or completed.
As our team has begun testing code, useful sections of it have been added to the repository for reference during future development of the full ground station software.

\subsubsection{Problem Statement Document}
A thorough problem statement document has been created by the group.
The document helps to direct the group and gives a high level view of the scope and goals for the project going forward.
Work on the document began on October 17th, a rough draft of this document was completed on October 10th and the final draft was completed and delivered to the client on October 20th.
The problem statement was approved by the client via email on October 24th.

\subsubsection{Requirements Document}
The requirements document lays out tasks that have to be completed in order for the project to be considered successful.
The document also includes a Gantt chart that serves as a rough time table and dependencies for each module that must be completed.
By following this document and completing each task on time, the team can be sure to complete the software within the required timetable.
Writing of the document began on October 26th.
A rough draft was completed on October 27th and a final version of the requirements document was delivered to the client for review on November 3rd.
The client officially approved the requirements document on November 3rd.

\subsubsection{Technology Review Documents}
The technology review documents serve as research for the technologies required to complete the project successfully.
Three documents were created, one by each member of the team.
The documents review technologies for the following aspects: 

\vspace{1em}
\begin{tabular}{| p{0.3\linewidth} | p{0.3\linewidth} | p{0.3\linewidth} |}
% Table headings
\hline\bf Corwin Perren & \bf Chris Pham & \bf Ken Steinfeldt \\\hline


\begin{itemize}
\item Robotics Framework
\item Communication Technologie\-s
\item Joysticks
\end{itemize}

&
\begin{itemize}
\item Application/GUI Framewor\-ks
\item Arm Visualization
\item Mapping
\end{itemize}

&
\begin{itemize}
\item Operating Systems
\item Hardware
\item Ground Station Deployment
\end{itemize}\\\hline
\end{tabular}
\vspace{1em}

Each team member's technology review was completed by November 21st.

\subsubsection{Software Design Document}
The Software Design Document (SDD) serves as a comprehensive plan for project completion, supplying an in-depth review of the requirements and plans to fulfill them.
Work began on the SDD on November 30th and the document was completed on December 1st. 
The SDD has not yet been submitted to the client for review and approval but will be in the near future.