\subsection{Summary}
The primary focus for the last ten weeks has been design and preparation for the ground station project.
In preparing the required documents and submitting the completed documents to our client we, also ensure that the team and the client are in agreement about the development of the ground station software.
Each document is built on the previous document as the team and client have developed a more thorough understanding of the requirements of the software that we will produce.
First, the problem statement laid out a broad understanding of what the problem to be solved was, helping to focus the scope of the project.
By defining the problem to be solved, our team was able to write the requirements document.
The requirements document states what solutions are needed in order to accomplish the problems previously defined in the problem statement.
With the requirements defined the team was able to research the best tools available to fulfill the stated requirements.
The technology review lays out several possible tools available, each able to fulfill a requirement.
The research required in order to complete the technology review allowed the team to not only attain a better grasp on technological problems, likely to present themselves during development, but also to choose tools that will be used as development progresses.
With all of the previous documents written the team was able to put together a comprehensive design document that will serve to guide development.
In addition to the creation of the necessary design documents, the team also gained access to the repository that will retain the development code.
All work completed in the last ten weeks accomplishes one overarching task, that is, laying the foundation for the project.
Going forward, the foundation we have created will ensure that our team and the client are on the same page, the project is completed to the specifications required by our client, and the project is completed in a timely manner.